Adopting agile in the large: motivations, success factors and challenges

### 2014-04-24 journal/article.tex
Reasons to change: management problems

% * Timeliness, accuracy
% 
% [P15]
% The number of releases needed to be increased, for accuracy

>>>>

\subsubsection{Internal issues}

The internal issues relate to how software development is managed in the
organization. In many organizations the project management practice was in a
state of dysfunction, and it needed to be corrected. Management problems were
for instance constantly recurring crisis events [P30], managers ignoring
prioritization of tasks [P38], and reluctance towards focusing on delivering
business value [P49]. Some cases stated that projects simply failed [P21]. Some
organizations wanted to improve generic project management practice, such as
risk management [P8], management of offshoring [P38], and improving the quality
of life of team members [P44]. Several organizations were growing and
experienced that the old development method did not scale up [P16, P50, P51].
There was also a desire to improve team motivation and commitment, and
collaboration between management and developers [P39].

Command and control style management where ``a few people, usually those
farthest from the action, made the decisions without directly involving the
developers doing the actual work'' [P44] was brought up as a problem. For
instance, schedules could be dictated by management, and teams had to comply to
them regardless of the workload [P9]. As a result teams were overworked and
needed stretch far to finish projects on time. Low morale and motivation were
identified as problems that needed to be fixed, and agile was seen as a solution
[P25, P30, P40].

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
